Thesis Draft

### 2015-09-30 chapter4.tex
artwork notebook.
Former-commit-id: c386004a5bc2735f3aa04da477cbb77fd36c6831

>>>>

\subsection{How I reached to notebook?}
Actually I have been collecting same materials that are used in my project before the thesis work. In my mind there is always belief that I can I find something useful for them. (In that time my main evaluation was to create useful object for my need.) Later it turned to an artwork. Before the thesis I also produce the notebooks for myself. However what is changed in thesis. First my approach to the trash is a little bit deeper. What is added to the notebooks. I started to use also used papers. for the cover of the notebook, I use more different materials. more close to collage. production method changed. and I started to collect different things, from different places. My realization increased. I organized my close friends and others to collect or save their trash for me. I discovered some points. their differences.

\textbf{Why notebook?} Because I already do it. So What I didn't change it. It is the best one or no to change it. I love idea of carrying notebook with near of you. I have also save my notebooks. I don't throw away them. A notebook is actually is a work of you. It carries your signature. It is one of best gift to give someone. Because it is a combination of your work and the other peoples works. It is co-authored work. Actually there is also a part of people who throw away this peace. Actually the best part of it the transformation is not finishes after my creation of notebook. It continues with the usage of it. How it turned to is not actually uncertain. Therefore it is very appropriate of my idea that transforming trash is increases the diversity.

\textbf{What is different from industrial notebooks?} Handmade, from trash. an alternative to other versions. every one have different stories, they are different in visuals (but the others are also different.) What makes them different is not clear actually. Does it have to be different? Yes. The production method is different. You pay no money. There is different with gift notebooks from companies. This notebooks call to you change the destiny of trash together.
